### 2016-07-26 sections/image_texts/col3byall_org.tex
# Conflicts: #	sections/image_texts/all.tex

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}

@@

    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, the result from gradually increasing the dimension of the input data from Fig.~\ref{fig: only_pahs} to 25. The order of the input data is the same as the order in Fig.~\ref{fig: cor_cluster1}.}

>>>>

        \includegraphics[width=54mm, height=38mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
        \caption{Input data: data from Fig.~\ref{fig: only_pahs} and \halpha}

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and11_dist} and \oiii}

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and12_dist} and \sii}

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and13_dist} and IRAC~5.7~$\mu$m emission}

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and14_dist} and PACS~100~$\mu$m emission }

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and15_dist} and SPIRE~250~$\mu$m emission }

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and16_dist} and SPIRE~350~$\mu$m emission }

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and17_dist} and SPIRE~500~$\mu$m emission }

@@

         \caption{Input data: data from Fig.~\ref{fig: col3and18_dist} and L$_{{\mathrm Dust}}$}

@@

          \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and M$_{{\mathrm Dust}}$}

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and20_dist} and SFR}

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and21_dist} and M$_{{\mathrm Stars}}$}

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and22_dist} and L$_{{\mathrm TIR}}$}

@@

        \caption{Input data: data from Fig.~\ref{fig: col3and23_dist} and M$_{{\mathrm Total gas}}$}

@@

        \includegraphics[width=\textwidth ]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and M$_{{\mathrm RHI}}$}

@@

    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result from increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually. The order of input data is the same as order of data in Fig.~\ref{fig: cor_cluster1}.}
